---
title: Stock Report
date: today
date-format: long
published-title: produced
format: email
attachments:
  - data.csv
email-preview: true
---

## Report for GSPC

```{r, echo=TRUE, message=FALSE}
library(DT)
library(formattable)
library(ggthemes)
library(quantmod)
library(dplyr)
library(plotly)
library(xts)
```


```{r}
#| eval: false
#| echo: false

# Cached data (gspc.csv) is used by default. To refresh it, set the `eval`
# option above to true to pull fresh data from Yahoo Finance, render once,
# then set it back to false.

prices <- round(getSymbols("^GSPC", auto.assign = FALSE, src = "yahoo"), 2)
close <- Cl(xts::last(prices))
open <- Op(xts::last(prices))

prices_df <- prices %>%
  as_tibble() %>%
  mutate(
    Date = index(prices),
    Direction = ifelse(GSPC.Close >= GSPC.Open, 'Increasing', 'Decreasing')
  )

readr::write_csv(prices_df, "gspc.csv")
```


```{r}
prices_df <- readr::read_csv("gspc.csv")
recent <- slice_max(prices_df, order_by = Date, n = 90)
latest_date <- max(prices_df$Date)

last_two <- prices_df |> slice_max(order_by = Date, n = 2) |> arrange(Date)
close <- last_two$GSPC.Close[2]
change <- round(close - last_two$GSPC.Close[1], 2)
```

The index closed `r ifelse(change > 0, "up", "down")` at `r close` points.

### Price History

The chart below is made with the `quantmod` and `plotly` R packages. The price history is read from a cached `gspc.csv` file, which can be refreshed from Yahoo Finance.


```{r build_plot, echo=TRUE, warning=FALSE, message=FALSE}
fig1 <- plot_ly(prices_df) %>%
  add_trace(
    type = "candlestick", x = ~Date, name = "GSPC",
    open = ~GSPC.Open, close = ~GSPC.Close,
    high = ~GSPC.High, low = ~GSPC.Low,
    increasing = list(line = list(color = '#17BECF')),
    decreasing = list(line = list(color = '#7F7F7F'))
  ) %>%
  layout(yaxis = list(title = "Price"))

fig2 <- plot_ly(prices_df) %>%
  add_bars(
    x = ~Date, y = ~GSPC.Volume, name = "GSPC Volume",
    color = ~Direction, colors = c('#17BECF', '#7F7F7F')
  ) %>%
  layout(yaxis = list(title = "Volume"), xaxis = list(title = ""))

subplot(
  fig1, fig2, heights = c(0.7, 0.2), nrows = 2,
  shareX = TRUE, titleY = TRUE
) %>%
  layout(
    hovermode = "x", margin = list(t = 80),
    title = paste("GSPC from", min(prices_df$Date), "to", max(prices_df$Date)),
    xaxis = list(
      rangeselector = list(
        x = 0, y = 1, xanchor = 'left', yanchor = "top",
        visible = TRUE, font = list(size = 9),
        buttons = list(
          list(count = 1, label = 'RESET', step = 'all'),
          list(count = 1, label = '1 YR', step = 'year', stepmode = 'backward'),
          list(count = 3, label = '3 MO', step = 'month', stepmode = 'backward'),
          list(count = 1, label = '1 MO', step = 'month', stepmode = 'backward')
        )
      )
    ),
    legend = list(
      x = 1, y = 1, xanchor = 'right',
      orientation = 'h', font = list(size = 10)
    )
  )
```

### Raw Data

The table below displays the daily price data for the index, with volume shown in millions. A concise, interactive table is created with the `DT` package.


```{r show_data, echo=TRUE}
recent %>%
  mutate(GSPC.Volume = GSPC.Volume / 1000000) %>%
  datatable() %>%
  formatRound(c("GSPC.Open", "GSPC.High", "GSPC.Low", "GSPC.Close"), digits = 2) %>%
  formatRound("GSPC.Volume", digits = 0)
```

## Downloadable Data

This report also writes the recent data to a CSV file and includes it as a downloadable attachment, so stakeholders can grab the underlying numbers.

```{r write_csv, echo = FALSE, include = FALSE}
write.csv(recent, file = "data.csv")
```

[Link to CSV](data.csv)

## Email

This report also produces an email that is sent to key stakeholders with summary
information.

::: {.email}

```{r compute_subject, warning = FALSE, message = FALSE, echo = FALSE}
subject <- sprintf("GSPC is %s by %g points (%s)",
        ifelse(change > 0, "up", "down"),
        abs(change),
        format(latest_date, "%B %d, %Y"))
```

::: {.subject}
`r subject`
:::

# Stock Update

Hello Team,

Here are the latest **GSPC** index levels as of `r format(latest_date, "%B %d, %Y")`:

```{r, echo = FALSE}
price_new <- prices_df |>
  arrange(Date) |>
  mutate(change = GSPC.Close - lag(GSPC.Close)) |>
  slice_tail(n = 10) |>
  select(Date, open = GSPC.Open, close = GSPC.Close, change)

# include a table with the index levels
format_table(
    x = as.data.frame(tail(price_new)),
    list(
      change = formatter(
        "span",
        style = x ~ ifelse(
          x > 0,
          formattable::style(color = "green"),
          formattable::style(color = "red")))
    )
  )
```

The historical trend is shown below:

```{r, echo = FALSE, message = FALSE}
# include a plot with the price data
ggplot(recent) +
  aes(Date, GSPC.Adjusted) +
  geom_smooth() +
  theme_fivethirtyeight() +
  labs(
    title = sprintf("%s Adjusted Close", "GSPC")
  )
```

Let me know if you have any questions.

Best,

Team Lead

:::
