---
title: GSPC Report
output:
  html_document:
    code_folding: hide
---
  
```{r setup, include=FALSE}
library(blastula)
library(DT)
library(formattable)
library(ggthemes)
library(quantmod)
library(dplyr)
library(plotly)
```

```{r refresh_data, eval=FALSE, echo=FALSE}
# Cached data is used by default. To refresh gspc.csv, set eval=TRUE to pull
# fresh data from Yahoo Finance, render once, then set eval=FALSE again.
prices <- round(getSymbols("^GSPC", auto.assign = FALSE, src = "yahoo"), 2)

prices |>
  as_tibble() |>
  mutate(
    Date = index(prices),
    Direction = ifelse(GSPC.Close >= GSPC.Open, 'Increasing', 'Decreasing')
  ) |>
  write.csv("gspc.csv", row.names = FALSE)
```

```{r load_data, include=FALSE}
prices_df <- read.csv("gspc.csv")
prices_df$Date <- as.Date(prices_df$Date)

prices <- xts::xts(
  as.matrix(prices_df[, c("GSPC.Open", "GSPC.High", "GSPC.Low", "GSPC.Close", "GSPC.Volume", "GSPC.Adjusted")]),
  order.by = prices_df$Date
)

recent <- xts::last(prices, n = 90)
latest_date <- max(prices_df$Date)

last_two_closes <- as.numeric(Cl(xts::last(prices, n = 2)))
close <- last_two_closes[2]
change <- round(close - last_two_closes[1], 2)
pct_change <- abs(change) / last_two_closes[1] * 100
```

# GSPC Report as of `r format(latest_date, "%B %d, %Y")`

## Summary{.tabset}

The index closed `r ifelse(change > 0, "up", "down")` at `r close` points.


### Price History

The chart below is made with the `quantmod` and `plotly` R packages. The price history is read from a cached `gspc.csv` file, which can be refreshed from Yahoo Finance.


```{r build_plot, echo=TRUE, warning=FALSE, message=FALSE}
fig1 <- plot_ly(prices_df) |>
  add_trace(
    type = "candlestick", x = ~Date, name = "GSPC",
    open = ~GSPC.Open, close = ~GSPC.Close,
    high = ~GSPC.High, low = ~GSPC.Low,
    increasing = list(line = list(color = '#17BECF')),
    decreasing = list(line = list(color = '#7F7F7F'))
  ) |> 
  layout(yaxis = list(title = "Price"))

fig2 <- plot_ly(prices_df) |>
  add_bars(
    x = ~Date, y = ~GSPC.Volume, name = "GSPC Volume",
    color = ~Direction, colors = c('#17BECF', '#7F7F7F')
  ) |>
  layout(yaxis = list(title = "Volume"), xaxis = list(title = ""))

subplot(
  fig1, fig2, heights = c(0.7, 0.2), nrows = 2,
  shareX = TRUE, titleY = TRUE
) |>
  layout(
    hovermode = "x", margin = list(t = 80),
    title = paste("GSPC from", min(prices_df$Date), "to", max(prices_df$Date)),
    xaxis = list(
      rangeselector = list(
        x = 0, y = 1, xanchor = 'left', yanchor = "top",
        visible = TRUE, font = list(size = 9),
        buttons = list(
          list(count = 1, label = 'RESET', step = 'all'),
          list(count = 1, label = '1 YR', step = 'year', stepmode = 'backward'),
          list(count = 3, label = '3 MO', step = 'month', stepmode = 'backward'),
          list(count = 1, label = '1 MO', step = 'month', stepmode = 'backward')
        )        
      )
    ),
    legend = list(
      x = 1, y = 1, xanchor = 'right',
      orientation = 'h', font = list(size = 10)
    )
  )
```

### Raw Data

The table below displays the daily price data for the index, with volume shown in millions. A concise, interactive table is created with the `DT` package.

  
```{r show_data, echo=TRUE}
recent |>
  as_tibble() |>
  mutate(GSPC.Volume = GSPC.Volume / 1000000) |>
  datatable() |>
  formatRound(c("GSPC.Open", "GSPC.High", "GSPC.Low", "GSPC.Close"), digits = 2) |>
  formatRound("GSPC.Volume", digits = 0)
```

## Downloadable Data

This report also writes the recent data to a CSV file and registers it as a downloadable output, so stakeholders can grab the underlying numbers.

```{r write_csv, echo=TRUE}
fname <- sprintf("%s.csv", Sys.Date())
write.csv(recent, file = fname)
rmarkdown::output_metadata$set(rsc_output_files = list(fname))
```

[Link to CSV](`r fname`)

## Email

This report also produces an email that is sent to key stakeholders with summary
information if the daily change exceeds 1%.

```{r send_email, warning = FALSE, message = FALSE, echo = TRUE}
subject <- sprintf("GSPC is %s by %g points (%s)",
        ifelse(change > 0, "up", "down"),
        abs(change),
        format(latest_date, "%B %d, %Y"))

# If the change exceeds the threshold (1% by default), send an email to
# stakeholders with key results embedded directly in the email. Adjust the
# threshold below to control how large a move triggers a notification.
if (pct_change > 1) {
  render_connect_email(input = "stock-report-email.Rmd") |>
  attach_connect_email(
    subject = subject,
    attach_output = TRUE,
    attachments = c(fname)
)
} else {
  blastula::suppress_scheduled_email()
}
```
